\documentclass[a4paper,10pt]{article}

\usepackage{parskip} 
\usepackage{hologo}
\usepackage{fontspec}

% Other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage[scale=0.85, top=.5in, bottom=.5in]{geometry} %Adjust Margins

% Tabularx environment
\usepackage{tabularx}

% For lists within experience section
\usepackage{enumitem}

% Centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

% To prevent spillover of tabular into next pages
\usepackage{supertabular}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.42\textwidth}

% Custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

% CV Sections inspired by: 
% http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{1pt}{2pt}{2pt}

% For publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

% Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\color[HTML]{110223}%{1C033C}
\setlength\bibitemsep{1em}

% For social icons
\usepackage{fontawesome5}
% \usepackage{times}

% For underline
\usepackage[normalem]{ulem}

% Set main font
\setmainfont{TeX Gyre Heros}  % Ensure Arial is installed and supports required shapes

% Use a different font for small caps if Arial doesn't support it
% \setsansfont{Linux Biolinum O}  % Example of a font with small caps

\begin{document}

% Non-numbered pages
\pagestyle{empty} 

% Allow more flexible line breaking to avoid overfull/underfull boxes
\sloppy

\begin{tabularx}{\linewidth}{@{} C @{}}
\color[HTML]{1C033C} \Huge{Rahul Mishra} \\[4pt]
\\
\textcolor[HTML]{371e77}{{{{\faMapMarker} Delhi, India}} $|$}
\textcolor[HTML]{371e77}{{{{\faEnvelope} \href{mailto:rahul.mishra2003@gmail.com}{rahul.mishra2003@gmail.com}}} $|$}
\textcolor[HTML]{371e77}{{{\faMobile} +91 9953-666-534}} \\
\textcolor[HTML]{371e77}{\underline{{\raisebox{-0.05\height}{\faGithub} \href{https://github.com/arhsimluhar}{https://github.com/arhsimluhar}}}} $|$
\textcolor[HTML]{371e77}{\underline{{\raisebox{-0.05\height}{\faLinkedin} \href{https://linkedin.com/in/arhsimluhar}{https://linkedin.com/in/arhsimluhar}}}}
\end{tabularx}

\section{Summary}
Principal Software Engineer with 8+ years of experience architecting and scaling backend systems, desktop applications, distributed systems, and cloud native infrastructure. Proven leader in driving engineering excellence, system performance, cost optimization, and DevSecOps adoption. Passionate mentor and proactive advocate for secure, reliable, and scalable software design. \\


\section{Technical Skills}
\color[HTML]{1C033C}\textbf{Languages:} C/C++, Go, Python, Rust \\[3pt]
\color[HTML]{1C033C}\textbf{Cloud \& DevOps:} AWS, Docker, Jenkins, Terraform \\[3pt]
\color[HTML]{1C033C}\textbf{Databases \& Processing:} PostgreSQL, Hive, Redis, DynamoDB \\[3pt]
\color[HTML]{1C033C}\textbf{Frameworks \& Tools:} Django, Gin, Grafana, Looker, OpenTelemetry, Jira, CMake, Bash \\[3pt]


% Experience
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{{Autodesk, Bangalore}} \hfill \color[HTML]{371e77} Dec 2024 - Present \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Principal Software Engineer}}\ \hfill \color[HTML]{4B28A4} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Led a team of 6 engineers to deliver backend services on time by owning agile ceremonies (sprint planning, backlog grooming) and improving release velocity by 50\%.
        \item Advocated best practices in CI/CD, observability and secure-coding, resulting in 40\% reduction in post-deploy issues and improved audit compliance.
        \item Architected a distributed backend system for scalability and cost-efficiency—enabled 3x scale-out and reduced infra spend 25\% via optimized service decomposition.

    \end{itemize}
\end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{371e77}\textbf{\textit{Senior Software Engineer}}\ \hfill \color[HTML]{4B28A4} Nov 2019 - Nov 2024\\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Designed a telemetry-based license compliance system that detected 1M+ non-compliant users, enabling targeted enforcement, contributing to 60M+ in recovered revenue.
        \item Drove secure development practices as the team's Security Champion, aligning with enterprise security goals.
        \item Built a tampering detection system using secure hashing and telemetry triggers—cut software piracy by 70\% across distributed installations.
        \item Promoted engineering excellence across design, testing, and deployment pipelines.
    \end{itemize}
\end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{{Attivo Networks, Bangalore}} \hfill \color[HTML]{371e77} July 2016 - Nov 2019 \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Software Engineer}}\ \hfill \color[HTML]{4B28A4} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Engineered dynamic deception endpoints used by 100+ enterprise customers for threat detection.
        \item Reduced CI/CD flakiness by 60\% by optimizing Jenkins pipeline steps, improving release confidence and delivery frequency. 
        \item Re-architected legacy system into modular services with improved test coverage, reducing deployment time by 40\% and enabling parallel development. 
        \item Mentored junior engineers through onboarding, code reviews, and technical guidance—scaling team delivery velocity by 3x. 
              
    \end{itemize}
\end{minipage}
\end{tabularx}

% Education
\section{Education}
\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{\textcolor[HTML]{1C033C}{Shri Mata Vaishno Devi University, J\&K}} & 
\textcolor[HTML]{371e77}{Aug 2012 -- May 2016} \\
\end{tabularx}
\textcolor[HTML]{371e77}{B.Tech. in Computer Science and Engineering} $|$
\textcolor[HTML]{4B28A4} {\textbf{CGPA: 7.81/10}} \\

% Leadership and Volunteering
\section{Awards \& Certifications}
\begin{itemize}[leftmargin=1.5em, label={}]
    \item \textbf{Applause Recognition – Autodesk} \\
    Awarded for key contributions to renewals of client accounts valued at \$300 M.
    \item \textbf{Autobucks Awards – Autodesk} \\
    Recognized for leading strategic initiatives that drove measurable business and operational impact.
\end{itemize}

\end{document}
